Keynote: BadUSB-C: Revisiting BadUSB with Type-C

### 2021-05-28 asss21-keynote/main.tex
first version of the keynote

\setbeamertemplate{footline}[frame number]
\usefonttheme{serif}
\setmainfont{Times New Roman}
\setsansfont{DejaVu Sans}

@@

\title{BadUSB-C: Revisiting BadUSB with Type-C}
\author{\textit{Hongyi Lu}, Yechang Wu, Shuqing Li, You Lin, Chaozu Zhang Fengwei Zhang}
\institute{Southern University of Science and Technology}
\date{\today}

@@

			This mitigation requires user authentication before allowing external USB devices.
		\column{.35\linewidth}
			\begin{figure}
				\includegraphics[width=\columnwidth]{Figs/huawei.png}
			\end{figure}
	\end{columns}
\end{frame}
\section{Conclusion}
\begin{frame}{Conclusion}
	We summarize our work as follows.
	\begin{enumerate}
		\item We explore a new attack scheme leveraging the latest feature of USB protocol.
		\item We conduct real-life scenario study of sharing powerbank to test BadUSB-C efficiency.
		\item We propose novel mitigation for our BadUSB-C attack.
	\end{enumerate}
\end{frame}
\begin{frame}
	\vfill
	\begin{center}
		\Large
		\emph{Thank You!}
	\end{center}
	\vfill
	\usebeamerfont{institute} \url{{11712009,11711918,lisq2017,11711809,11712021}@mail.sustech.edu.cn}
		\\ \url{zhangfw@sustech.edu.cn}
\end{frame}

>>>>

\setbeamertemplate{footline}[frame number]
\usefonttheme{serif}
\setmainfont{Times New Roman}
%\setsansfont{DejaVu Sans}

@@

\title{Keynote: BadUSB-C: Revisiting BadUSB with Type-C}

\author{\textbf{Fengwei Zhang} \\\vspace{3pt}  \includegraphics[width=1.5cm]{name.jpg}}
\institute{COMPASS Lab, SUSTech\\ \vspace{5pt}
\includegraphics[width=1.5cm]{sustech-logo.jpeg}}
%\includegraphics[width=2cm]{logo.png}}

\date{June 7, 2021}

@@

			This mitigation requires user authentication before allowing external USB devices.
		\column{.35\linewidth}
			\begin{figure}
				\includegraphics[width=\columnwidth]{Figs/huawei.png}
			\end{figure}
	\end{columns}
\end{frame}
\section{Conclusion}
\begin{frame}{Conclusion}
	We summarize our work as follows.
	\begin{enumerate}
		\item We explore a new attack scheme leveraging the latest feature of USB protocol.
		\item We conduct real-life scenario study of sharing powerbank to test BadUSB-C efficiency.
		\item We propose novel mitigation for our BadUSB-C attack.
	\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Thank you!}
\begin{center}
{\huge Questions?}
\vspace{10pt}

zhangfw@sustech.edu.cn
\vspace{10pt}

\begin{figure}
\includegraphics[width=0.25\textwidth]{homepageqrcode.png}
\end{figure}

\vspace{-10pt}
\url{http://cse.sustech.edu.cn/faculty/~zhangfw/}

\end{center}
